\documentclass[12pt]{letter} 


\usepackage[margin=1in]{geometry}

\signature{Connor Briggs}

\begin{document}

\begin{letter}{\today}

  \opening{Dear Recruiter}

   My name is Connor Briggs, and I am interested in applying to {job position}. I am a recent chemistry graduate from Virginia Tech, and am looking to apply my skills in the real world. I already have much experience working in a lab setting from my time at Virginia Tech, and also from continuing research after graduation with Dr. Joseph Merola's lab. Over the course of my degree, I also worked with Dr. Daniel Crawford's lab to co-author a paper on quantum chemistry.
  
  
  My experience in chemistry gives me a unique edge when it comes to analyzing characterization data. Through the course work at Virginia Tech, I learned the theory behind several different forms of chromatography, and I performed many of them in my lab courses. I applied these analysis skills in my research with Dr. Merola, where I needed to assess the purity, identity, and structure of synthesized compounds. The curriculum at Virginia Tech also provided a background in biological applications of chemistry, with a bio-organic chemistry progression. This course work gave me a deeper understanding of how chemicals interact with cellular systems. My degree and subsequent research gave me experience in data analysis tools, especially Microsoft Office. Using these tools, I became familiar with analyzing raw data from instruments such as chromatographs.


  Thank you for taking the time to consider my application. I hope my skills and experiences will be a good fit for {place}. I look forward to hearing a response.
\closing{Sincerely,}
  
\end{letter}
\end{document}
