\documentclass[12pt]{letter} 


\usepackage[margin=1in]{geometry}

\signature{Connor Briggs}

\begin{document}

\begin{letter}{\today}

  \opening{Dear Recruiter}

   My name is Connor Briggs, and I am interested in applying to the open associate investigator role. I am a recent chemistry graduate from Virginia Tech, and am looking to apply my skills in the real world. I already have much experience working in a lab setting from my time at Virginia Tech, and also from continuing research after graduation with Dr. Joseph Merola's lab. Over the course of my degree, I also worked with Dr. Daniel Crawford's lab to co-author a paper on quantum chemistry.
  
  
   The curriculum at Virginia Tech for Bachelors of Science in chemistry is very heavily instrument-oriented. In many classes, I learned how to operate many different kinds of instruments, as well as their working principles; these include but are not limited to chromatographs with various detectors, various spectrophotometers, and nuclear magnetic resonance spectrometers. My classwork at Virginia Tech also focused heavily on polymers and their properties. In these courses, I learned not just how to make polymers, but also how they are characterized, what their properties imply, and environmental considerations when making and disposing of polymers.

   Outside of the coursework, I have much experience in research laboratories. In my work with Dr. Merola, I led an individual project investigating ring-opening reactions of substituted thiophene rings. However, I am still working on publishing the results. The analyses of the products that I made were done mainly through nuclear magnetic resonance, which seems to be important for the position to which I am applying.


  Thank you for taking the time to consider my application. I hope my skills and experiences will be a good fit for your team at Wilmington. I look forward to hearing a response.
\closing{Sincerely,}
  
\end{letter}
\end{document}
