\documentclass[12pt]{letter} 


\usepackage[margin=1in]{geometry}

\signature{Connor Briggs}
\address{Connor Briggs\\203 Whitmer Road\\Shippensburg, PA, 17257\\\\Phone: +1-(717)-860-9342\\Email: cgbriggs99@gmail.com}
%\location{cgbriggs99@gmail.com}

\begin{document}

\begin{letter}{Sepax Technologies, Inc.\\5 Innovation Way\\Newark, DE 19711}

  \opening{Dear Recruiter}

   My name is Connor Briggs, and I am interested in applying to the associate chemist position at Sepax. I am a recent chemistry graduate from Virginia Tech, and am looking to apply my skills in the real world.  I am a motivated individual, always with a positive attitude. My attention to detail is unmatched. I do well with team oriented work, but I am self-motivated enough to perform on my own.
  
  
   My experience with chemistry has taken me through various fields. While I was studying at Virginia Tech, I learned how to use various characterization instrumentation, including HPLC. I learned the ways of laboratory housekeeping and their importance. In my lab courses, I perfected standard purification techniques, such as chromatography and distillation. Record keeping was of utmost importance in the labs. In the lecture hall, I learned about the field of chemical manufacturing in my organic chemistry and material science courses. I learned documentation skills in my instrumental analysis course.


   While I was at Virginia Tech, I participated in research under two different professors. In Dr. Daniel Crawford's lab, I worked with graduate students on machine learning projects. I contributed thousands of lines of code to the group, and assisted on the writing of a publication in a major journal. After I graduated, I worked with Dr. Joseph Merola, performing a variety of experiments to study ring-opening reactions of over 10 different substituted thiophenes. Here, I put my chemistry and written communications skills to the test. In the near future, I will be publishing the results in a journal.


  Thank you for taking the time to consider my application. I hope my skills and experiences will be a good fit for the Newark team at Sepax. I look forward to hearing a response.
\closing{Sincerely,}
  
\end{letter}
\end{document}
