% Curriculum Vitae
% Author: Connor Briggs

% Use the moderncv class to typeset.
\documentclass{moderncv}


% I like blue. Also, casual breaks pdflatex.
\moderncvtheme[blue]{classic}

% Set the margins to something reasonable.
\usepackage[margin=1in]{geometry}
\recomputelengths % this has to be here according to moderncv docs.

% Get the github symbols.
\usepackage{fontawesome}

\usepackage{needspace}

\usepackage{tcolorbox}


%\newcommand{\cvskill}[1]{\tcbox[colframe=color1, valign=center, before=, after=\hfill, height=1.1\baselineskip, boxsep=2pt, left=2pt, right=2pt]{#1}}

% Personal info.
\firstname{Connor}
\lastname{Briggs}
\address{203 Whitmer Rd.}{Shippensburg, PA, 17257}
\phone{+1-(717)-860-9342}
\email{cgbriggs99@gmail.com}
\social[linkedin]{connor-briggs-1ba514214}
\social[github]{cgbriggs99}

\begin{document}
% Add title with personal info.
\makecvtitle

% Needs the \Needspace* so that section titles don't become orphans.
\Needspace*{4\baselineskip}
\section{Research Interests}
Applications of machine learning to quantum chemistry.

\Needspace*{4\baselineskip}
\section{Education}
\cventry{2017--2022}{B.S. in Chemistry with Mathematics Minor}{Virginia Tech}{Blacksburg, VA}{\textit{2.75 GPA}}{My first year at VT I struggled to adjust, and I ended my first semester with a 1.96. In my second and third years, I worked hard and my GPA shot up to a 2.67. When lockdowns started, I struggled to adjust to online learning, and my GPA stagnated, ending my fourth year with a 2.66. With the return to in-person instruction, I finished out my time here with a 2.75, significantly higher than what I started with.}
\cventry{2012--2017}{High School Diploma}{Shippensburg Area Senior High School}{Shippensburg, PA}{}{During high school, I enrolled in several college courses in computer science, chemistry, physics, math, and electrical engineering.}

\Needspace*{4\baselineskip}
\section{Employment History}
\cventry{2018--2021}{Salesperson}{Sheetz}{Shippensburg, PA}{}{Prepared food, handled transactions, and handled maintenance jobs around the store.}

\Needspace*{4\baselineskip}
\section{Languages}
\cvlanguage{English}{Native speaker}{}
\cvlanguage{French}{Conversational proficiency}{}
\cvlanguage{German}{Conversational proficiency}{}
\cvlanguage{Esperanto}{Conversational proficiency}{}

\Needspace*{4\baselineskip}
\section{Skills}
\cvcomputer{Coding Lanugages}{C/C++, Python, CUDA C/C++, GNU Make, Bash, Java, \LaTeX, \TeX, FORTRAN, x86 Assembler, Common Lisp}{Operating Systems}{GNU/Linux (Debian, Ubuntu, Linux Mint, CentOS), Windows}
\cvcomputer{Technical Skills}{Psi4, Gaussian, QCFractal, Git, Microsoft Office Suite, Google Office Suite, LibreOffice Suite, OpenMP, Super Computing, Quantum Computing}{Chemistry}{Quantum chemistry, Organic synthetic techniques, Inorganic Synthetic Techniques, Glovebox use, Schlenk line manipulations, NMR, IR, UV/Vis, Gas Chromatography, GC/MS, X-Ray Diffraction}

\Needspace*{4\baselineskip}
\section{Awards}
\cventry{2022}{ACS Undergraduate Award in Inorganic Chemistry}{ACS Division of Inorganic Chemistry}{}{}{This award was given for my research on thiophene ring-opening reactions.}

\Needspace*{4\baselineskip}
\section{Research Experience}
\cventry{2017--2022}{Undergraduate Research}{Virginia Tech}{Blacksburg, VA}{}{Worked under Dr. T. Daniel Crawford in his theory lab at Virginia Tech.}

\Needspace*{4\baselineskip}
\section{Teaching Experience}
\cventry{2015--2020}{Tutoring}{}{}{}{Tutored several students in chemistry and mathematics.}

\Needspace*{4\baselineskip}
\section{Current Projects}
\cventry{2022}{Ring insertions of iridium(I) complexes into substituted thiophene rings}{}{}{}{For my capstone project, I performed several ring insertion reactions of tris(trimethylphosphine)(1,5-cyclooctadiene)iridium(I) chloride into several substituted thiophenes to investigate how different substituents would affect the insertion. I then worked with Dr. Joseph Merola of the Virginia Tech Department of Chemistry to finish the project, and I hope to have the results published by the end of Summer 2022.}

\Needspace*{4\baselineskip}
\nocite{*}
\bibliographystyle{plain}
\bibliography{../pubs}

\end{document}
