\documentclass[12pt]{letter} 


\usepackage[margin=1in]{geometry}

\signature{Connor Briggs}
\author{Connor Briggs}
\address{Connor Briggs\\203 Whitmer Rd.\\Shippensburg, PA 17257\\cgbriggs99@gmail.com\\+1-(717)-860-9342}

\begin{document}

\begin{letter}{Advanced Testing Laboratory\\Martinsburg, WV 25401}

  \opening{Dear Recruiter}

   My name is Connor Briggs, and I am interested in applying to the analytical~chemist position. I am a recent chemistry graduate from Virginia Tech, and am looking to apply my skills in the real world. I already have much experience working in a lab setting from my time at Virginia Tech, and also from continuing research after graduation with Dr. Joseph Merola's lab. Over the course of my degree, I also worked with Dr. Daniel Crawford's lab to co-author a paper on quantum chemistry.


   At Virginia Tech, I performed several experiments to investigate analytical chemistry. I learned how to use several common techniques, such as gas chromatography and various types of spectroscopy. I also learned the principles of operation of several common instruments in my instrumental analysis courses. Outside of the coursework, I worked in a research laboratory performing inorganic syntheses, and analyzing the products using standard methods such as NMR spectroscopy.
  
  
  Thank you for taking the time to consider my application. I hope my skills and experiences will be a good fit for your Martinsburg team. I look forward to hearing a response.
\closing{Sincerely,}
  
\end{letter}
\end{document}
