 % Curriculum Vitae
% Author: Connor Briggs

% Use the moderncv class to typeset.
\documentclass{moderncv}

% I like blue. Also, casual breaks pdflatex.
\moderncvtheme[black]{classic}

% Set the margins to something reasonable.
\usepackage[margin=1in]{geometry}
\recomputelengths % this has to be here according to moderncv docs.

% Get the github symbols.
\usepackage{fontawesome}

\usepackage{needspace}

\usepackage{tcolorbox}

%\newcommand{\cvskill}[1]{\tcbox[colframe=color1, valign=center, before=, after=\hfill, height=1.1\baselineskip, boxsep=2pt, left=2pt, right=2pt]{#1}}

% Say Selected Publications instead of Publications.
\renewcommand{\refname}{Selected Publications}

% Personal info.
\firstname{Connor}
\lastname{Briggs}
\address{203 Whitmer Rd.}{Shippensburg, PA, 17257}
\phone{+1-(717)-860-9342}
\email{cgbriggs99@gmail.com}
\social[github]{cgbriggs99}
\social[linkedin]{connor-briggs-1ba514241}

\begin{document}
% Add title with personal info.
\makecvtitle

% Needs the \Needspace* so that section titles don't become orphans.
\Needspace*{4\baselineskip}
\section{Statement}
Chemistry graduate from Virginia Tech with five years scientific research experience. Looking for a position as a process chemist. Work well in a fast-paced environment. Strong~work~ethic with a positive attitude. Great attention to detail. Collaborative, but can also work independently. Flexibility to adapt to any environment.

\section{Education}
\cventry{08/2017 - 05/2022}{B.S. in Chemistry, Mathematics Minor}{Virginia Polytechnic Institute and State University (Virginia Tech)}{Blacksburg, VA, 24060}{GPA: 2.75}{Completed a bachelor's degree in chemistry. While taking classes, I also worked with Dr. Daniel Crawford's research group to conduct research, where I contributed to the publication of one paper, and wrote thousands of lines of code. I also learned the importance of confidentiality in science.}
\cventry{08/2013 - 05/2017}{High School Diploma}{Shippensburg Area Senior High School}{Shippensburg, PA, 17257}{}{}

\section{Skills}
\cvlistdoubleitem{Organic Chemistry}{X-ray Spectroscopy}
\cvlistdoubleitem{Laboratory Equipment}{Platinum Group Metal Chemistry}
\cvlistdoubleitem{Analytical Chemistry}{Instrumental Analysis}
\cvlistdoubleitem{Plating}{Statistical Process Control}
\cvlistdoubleitem{Laboratory Housekeeping}{Written Communications}
\cvlistdoubleitem{Prototype Design}{Laboratory Instrumentation}
\cvlistdoubleitem{Team Building}{Performing Experiments}
\cvlistdoubleitem{Interpersonal Skills}{Attention to Detail}
\cvlistdoubleitem{Microsoft Office Suite}{Scientific Communication}
\cvlistdoubleitem{Iridium Chemistry}{Sample Preparation and Testing}
\cvlistdoubleitem{Catalytic Chemistry}{Analysis Techniques}
\cvlistdoubleitem{Data Management and Interpretation}{Lab Maintenance}

\section{Work Experience}
\cventry{05/2022 - 07/2022}{Student Researcher}{Virginia Tech}{Blacksburg, VA, 24061}{}{Led an individual research project under the supervision of Dr. Joseph Merola. Performed over 20 reactions and investigated the ring-opening reactions of several different substituted thiophenes. The study investigated over 10 different rings, and involved the synthesis of a common iridium catalyst.}

\cventry{05/2018 - 07/2021}{Salesperson}{Sheetz}{Shippensburg, PA, 17257}{}{Worked as a cashier, serving hundreds of customers daily. Also spent some time as a line cook, with high order accuracy and speed, rarely dipping below a success rate of 60\%.}

\section{Awards}
\cventry{07/2022}{ACS Undergraduate Award in Inorganic Chemistry}{ACS Division of Inorganic Chemistry}{}{}{This award is given to undergraduate students who display excellence in inorganic chemistry, especially through research and coursework.}

\section{Projects}
\cventry{05/2022 - 07/2022}{Thiophene Ring Insertions}{Virginia Tech}{}{}{In this project, I performed experiments to deduce the mechanics of a ring insertion reaction between tris(trimethylphosphine)(1,5-cyclooctadiene)iridium(I) chloride and several thiophene derivatives.}

\Needspace*{4\baselineskip}
\nocite{MLQM}
\bibliographystyle{plain}
\bibliography{../pubs}

\end{document}
